Experiments and Modeling of the Autoignition of Methyl Pentanoate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-09-27 revision-1/revised-paper/methyl-valerate.tex
Final updates of the revision!

\begin{center}
    \captionsetup{type=figure}
    \includegraphics{figures/ignition_delay_definition.pdf}
    \caption{Definition of the ignition delays used in this work. The experiment in this figure is
    conducted for a \(\phi=2.0\) mixture with \mbox{\(\ce{Ar}/(\ce{N2}+\ce{Ar})=0.5\)},
    \(P_0=\SI{0.7806}{\bar}\), \(T_0=\SI{373}{\K}\), \(P_C=\SI{14.92}{\bar}\), \(T_C=\SI{720}{\K}\),
    \(\tau=\SI{27.56\pm0.89}{\ms}\), and \(\tau_1=\SI{16.60\pm0.46}{\ms}\). The non-reacting
    pressure traces by replacing \ce{O2} with \ce{N2} is also shown for reference.}
    \label{fig:ign-delay-def}
\end{center}

@@

At \SI{15}{\bar}, the experimental overall ignition delays are under-predicted by the
\citet{Dievart2013} model for the three equivalence ratios shown. For the \(\phi =\)
\numlist{0.25;0.5} conditions, the model appears to be predicting an NTC region of the overall
ignition delays as the temperature decreases, as judged by the increasing curvature of the
simulations, although such a trend is not observed apparent in the figure. However, at \(\phi =
2.0\), the model does not predict the presence of an NTC region, although one is present in the
experiments. Nonetheless, the agreement seems to be improving as the temperature is decreased.
Comparing the \citet{Dievart2013} model to the stoichiometric data at \SI{30}{\bar}, we find a
similar trend as the \(\phi=2.0\), \(P_C=\SI{15}{\bar}\) data. The model does not predict the NTC
region found experimentally for the \(\phi = 1.0\), \(P_C=\SI{30}{\bar}\) experiments, but the
agreement improves as the temperature decreases. Interestingly, two-stage ignition is predicted for
all of the \(\phi=1.0\) and \(\phi=2.0\) data shown in \cref{fig:simulation-comparison}. However,
the first-stage ignition delays are \SIrange{0.1}{0.5}{\ms} less than the overall ignition delays,
and are not shown on \cref{fig:simulation-comparison} because they are nearly indistinguishable from
the overall ignition delay.

>>>>

\begin{center}
    \captionsetup{type=figure}
    \includegraphics{figures/ignition_delay_definition.pdf}
    \caption{Definition of the ignition delays used in this work. The experiment in this figure is
    conducted for a \(\phi=2.0\) mixture with \mbox{\(\ce{Ar}/(\ce{N2}+\ce{Ar})=0.5\)},
    \(P_0=\SI{0.7806}{\bar}\), \(T_0=\SI{373}{\K}\), \(P_C=\SI{14.92}{\bar}\), \(T_C=\SI{720}{\K}\),
    \(\tau=\SI{27.56\pm0.89}{\ms}\), and \(\tau_1=\SI{16.60\pm0.46}{\ms}\). The non-reacting
    pressure trace by replacing \ce{O2} with \ce{N2} is also shown for reference.}
    \label{fig:ign-delay-def}
\end{center}

@@

At \SI{15}{\bar}, the experimental overall ignition delays are under-predicted by the
\citet{Dievart2013} model for the three equivalence ratios shown. For the \(\phi =\)
\numlist{0.25;0.5} conditions, the model appears to be predicting an NTC region of the overall
ignition delays as the temperature decreases, as judged by the increasing curvature of the
simulations, although such a trend is not observed for the experimental data. However, at \(\phi =
2.0\), the model does not predict the presence of an NTC region, although one is present in the
experiments. Nonetheless, the agreement seems to be improving as the temperature is decreased.
Comparing the \citet{Dievart2013} model to the stoichiometric data at \SI{30}{\bar}, we find a
similar trend as the \(\phi=2.0\), \(P_C=\SI{15}{\bar}\) data. The model does not predict the NTC
region found experimentally for the \(\phi = 1.0\), \(P_C=\SI{30}{\bar}\) experiments, but the
agreement improves as the temperature decreases. Interestingly, two-stage ignition is predicted for
all of the \(\phi=1.0\) and \(\phi=2.0\) data shown in \cref{fig:simulation-comparison}. However,
the first-stage ignition delays are \SIrange{0.1}{0.5}{\ms} less than the overall ignition delays,
and are not shown on \cref{fig:simulation-comparison} because they are nearly indistinguishable from
the overall ignition delay.
